---
title: "Oct 28 Meeting"
output: html_notebook
---

```{r merged into}
df_change %>% 
  filter(reason_short1 == 'merged into') %>%
  mutate(target = reason1) %>%
  mutate(target = gsub('Merged with ([0-9]+) to form','',target)) %>%
  mutate(target = gsub('Changed to outpatient and merged with ([0-9]+) to form','',target)) %>%
  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r unit of other hosp}
df_change %>% 
  filter(reason_short1 == 'unit of other hosp') %>%
  mutate(target = reason1) %>%
  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r dissolution}
df_change %>% 
  filter(reason_short1 == 'dissolution') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r demerger}
df_change %>% 
  filter(reason_short1 == 'demerger') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

BUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUG
BUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUG
```{r demerged}
df_change %>% 
  filter(reason_short2 == 'demerged') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```
BUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUG
BUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUG

```{r duplicate}
df_change %>% 
  filter(reason_short1 == 'duplicate') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r merger result}
df_change %>% 
  filter(reason_short1 == 'merger result') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r ID change}
df_change %>% 
  filter(reason_short1 == 'ID change') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
