---
title: "readme"
author: "Wonjun Choi"
date: "2022-10-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Import Package, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(data.table, tidyverse, janitor, here)
```

```{r Cooper data, include=FALSE}
dat_cooper <- read_csv(paste0(here(),'/data/cooper-et-al/HC_ext_mergerdata_public.csv'))
```
```{r}
dat_cooper %>% select(id) %>% unique() %>% nrow()
```
There are 4776 unique `id` in the data of Cooper et al.

```{r include=FALSE}
for (v in variable.names(dat_cooper)){
  print(dat_cooper %>% select(v) %>% group_by_(v)%>% summarise(n=n()))
}
```
- HOSPN: not unique
- SYSID(matches to health care system file?): not unique
- SYSNAME: not unique, 2833 NA's
- (LAT,LONG): not unique -> see [lat,long is not unique]

```{r sysid is not unique, include=F}
# df_tmp1 <- df_tmp %>% group_by(SYSID) %>% summarise(n=n()) %>% right_join(df_tmp, by="SYSID")
# 
# df_tmp1 %>% filter(n>=2) %>% select(ID, SYSID, n)
# 
# # cross-check with cooper -- not meaningful in this stage...
# df_tmp2 <- dat_cooper %>% filter(year==2007)
# df_tmp2 <- df_tmp2 %>% group_by(sysid) %>% summarise(n=n()) %>% right_join(df_tmp2, by='sysid')
# 
# df_tmp2 %>% filter(n>=2) %>% select(id, sysid, n)
# 
# df_tmp1 %>% mutate(id=ID) %>% left_join(df_tmp2, by="id") %>% select(id, SYSID, n.x, n.y)
```
seems cooper et al. somehow pooled sysid==2...?

```{r lat,long is not unique}
# df_tmp %>% group_by(LAT,LONG) %>% summarise(n=n()) %>% left_join(df_tmp, by=c("LAT","LONG")) %>% filter(n >=2) %>% select(ID, n, LAT, LONG)
```

```{r}
dat_cooper %>% filter(year==2007) %>% nrow()
```


```{r ??}
# dat_cooper %>% filter(year==2007) %>% select(id) %>% unique()
# dat_cooper %>% group_by(sysid) %>% summarise(n_cooper=n()) %>% left_join(dat_cooper, by="sysid") %>% select(id, sysid, n_cooper) %>% mutate(ID = id) %>% left_join(df_tmp, by="ID") %>% select(ID, sysid, n_cooper)
```

# aha_data

```{r}
aha_data %>% names()
```
 
```{r}
# aha_data %>% filter(ID==6141740) 
# 6080001: deleted in 2013 bc not hospital, but added again.
#  => delete before deletion, and check again
```

```{r}
# source('data-code/tidy_aha_data.R')
```

```{r}
aha_data %>% filter(is.na(reason_short))
```

```{r}
df_left = tibble('ID'=c(1,2,3),
                 'reason1'=c(NA,'jaja',NA),
                 'reason2'=c(NA,NA,NA))
df_right = tibble('ID' = c(1,2),
                  'reason'=c('haha','lol'))
#print(df_left)
#print(df_right)

my_update <- function(data_left, data_right) {
  for (i_right in 1:nrow(data_right)) {  # for each ID in right
    ID <- data_right[i_right,'ID']
    i_left <- which(data_left$ID == ID[[1]])   # find index in left
  
    # find empty slot in left
    suffix <- 1 
    reason_s <- paste0('reason_short',suffix)
    while (is.na(data_left[i_left,reason_s]) == F) { 
      suffix <- suffix+1
      reason_s <- paste0('reason_short',suffix)
    }
    #vars = c('reason')
    vars = c('year', 'reason_short','reason')  # modify here
    for (v in vars) {
      v_s <- paste0(v, suffix)
      df_left[i_left, v_s] <- df_right[i_right, v]
    }
  }
  return(df_left)
}
```
```{r}
i_right = 1
ID <- df_right[1,'ID']
i_left <- which(df_left$ID == ID[[1]])

suffix <- 1
reason_s <- paste0('reason_short', suffix)

is.na(df_left[i_left, reason_s])[[1]] == F
```

```{r}
error_counter <- 0  # check data_right[error_counter,]
df_left_test <- df_left
del2007 <- 'aa'
err <- 0

my_update <- function(data_left, data_right) {
  for (i_right in 1:nrow(data_right)) {  # for each ID in right
    error_counter <<- i_right+1
    ID <- data_right[[i_right,'ID']]
    
    if (is.na(data_right[[i_right, 'del']])==F & 
        data_right[[i_right, 'year']]==2007 &
        !(ID %in% data_left$ID)) {
      del2007 <<- 'if'
      row <- data.frame('ID'=ID,
                        'year1'=2007,
                        'reason_short1'=data_right[[i_right,'reason_short']],
                        'reason1'=data_right[[i_right,'reason']])
      data_left <- bind_rows(row, data_left)
      df_left_test <<- data_left
    } else {
      del2007 <<- 'else'
      i_left <- which(data_left$ID == ID)   # find index in left
      err <<- 1
      
      # find empty slot in left
      suffix <- 1 
      reason_s <- paste0('reason_short',suffix)
      while (is.na(data_left[[i_left,reason_s]]) == F) { 
        suffix <- suffix+1
        reason_s <- paste0('reason_short',suffix)
      }
      #vars = c('reason')
      vars = c('year', 'reason_short','reason')  # modify here
      for (v in vars) {
        v_s <- paste0(v, suffix)
        data_left[i_left, v_s] <- data_right[i_right, v]
        df_left_test <<- data_left
      }
    }
  }
  return(data_left)
}
```

```{r}
df_right[[55,'del']]==1
```

```{r}
# aha_data %>% group_by(ID) %>% summarise(n=n()) %>% arrange(desc(n))
# maximum number of changes = 4

df_left <- df_hosp %>% select(ID) %>% unique() %>%
  mutate('year1' = NA, 'reason_short1' = NA, 'reason1' = NA,
         'year2' = NA, 'reason_short2' = NA, 'reason2' = NA,
         'year3' = NA, 'reason_short3' = NA, 'reason3' = NA,
         'year4' = NA, 'reason_short4' = NA, 'reason4' = NA,
         'year5' = NA, 'reason_short5' = NA, 'reason5' = NA) %>%
  mutate(ID2 = as.integer(ID),
         ID = ifelse(is.na(ID2)==F, ID2, ID)) %>%
  select(-c(ID2))

df_right <- aha_data

df_right <- df_right %>% 
  mutate(ID2 = as.integer(ID),
         ID = ifelse(is.na(ID2)==F, ID2, ID)) %>%
  select(-c(ID2))
# fifth is just a buffer.


df_change <- my_update(df_left, df_right)

df_test4 <- df_change %>% filter(is.na(reason_short4)==F)
```
```{r}
df_right[error_counter,]
```
```{r}
df_left %>% mutate(ID2 = as.integer(ID)) %>% filter(is.na(ID2)==T)
```

```{r}
df_right %>% mutate(ID2 = as.integer(ID)) %>% filter(is.na(ID2)==T)
```


```{r include=FALSE}
ID <- df_right[[error_counter,'ID']]
ID
```
```{r}
is.na(df_right[[error_counter, 'del']])&df_right[[error_counter,'year']]==2007

```

```{r}
df_left_test %>% filter(ID == "6710013")
```


```{r merged into}
df_change %>% 
  filter(reason_short1 == 'merged into') %>%
  mutate(target = reason1) %>%
  mutate(target = gsub('Merged with ([0-9]+) to form','',target)) %>%
  mutate(target = gsub('Changed to outpatient and merged with ([0-9]+) to form','',target)) %>%
  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r unit of other hosp}
df_change %>% 
  filter(reason_short1 == 'unit of other hosp') %>%
  mutate(target = reason1) %>%
  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r dissolution}
df_change %>% 
  filter(reason_short1 == 'dissolution') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r demerger}
df_change %>% 
  filter(reason_short1 == 'demerger') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

BUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUG
BUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUG
```{r demerged}
df_change %>% 
  filter(reason_short2 == 'demerged') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```
BUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUG
BUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUGBUG

```{r duplicate}
df_change %>% 
  filter(reason_short1 == 'duplicate') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r merger result}
df_change %>% 
  filter(reason_short1 == 'merger result') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

```{r ID change}
df_change %>% 
  filter(reason_short1 == 'ID change') %>%
  mutate(target = reason1) %>%
#  mutate(target = parse_number(target)) %>%
  select(ID,target)
```

Discuss this file with Ian